---
title: "ACE2_snp"
author: "Sarah Urbut"
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: no
  html_notebook: default
  html_document:
    df_print: paged
    toc: no
editor_options:
  chunk_output_type: console
---


## Organizing the data

First, we read in the data frame and organize it into a data frame of SNP-gene pair x tissues

```{r cars}
df= read.table("~/Downloads/gtexv8.tsv",sep="\t", header=TRUE)
df$z=df$slope/df$slope_se
head(df)
#df2=data.frame(df$z)
df2=data.frame(df$slope_se)
head(df2)
z=t(df2)

colnames(z)=df$tissue

n=sapply(colnames(z),function(x){
strsplit(x,"ACE2_")[[1]][2]})

colnames(z)=n

m=readRDS("~/Downloads/mfit_GTEX.rds")
tissues=names(m$fitted_g$Ulist)[31:79]
setdiff(tissues,colnames(z))
sapply(setdiff(tissues,colnames(z)),function(x){which(tissues==x)})


df=data.frame(t(c(z[,1:20],"Cells_Cultured_fibroblasts"=0,"Cells_EBV-transformed_lymphocytes"=0,z[,21:40],"Spleen"=0,z[,41:45],"Whole_Blood"=0)))

##check that they are the same

cbind(colnames(df),tissues)
install.packages(("mashr"))
```

## Computing Posteriors

Here, we run mash by fitting in the appropriate data frame (we need at least a 2 x R matrix, the hierarhical model fit (including covariance matrices, HM weights, and variance of residuals esimates) and then compute posteriors in the object *m2*.

```{r pressure, eval=FALSE}
df=as.matrix(read.table("../data/df.txt"))
library("mashr")
vhat=readRDS("vhatgtex.rds")
m=readRDS("mfit_GTEX.rds")
###mash needs at least a 2xR matrix, so rbind

d=rbind(df,df)
data.strong=mash_set_data(Bhat=d,alpha=1,V=vhat)
m2 = mash(data.strong, g=get_fitted_g(m), fixg=TRUE)
```

And now, we're ready to plot! Please my code in the *code* directory for an overview of metaplot and the normalization procedure to produce posterior betas from the EZ model which assumes effects scales with their standard errors.

```{r}
source("code/helper.R")
library("rmeta")
newfunc.2(1)

```



